Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-02-10 paper.tex
Added extra reference, reworded displacement/polarisation discussion and added new possible reversable faradaic reaction

\section{Displacement Parameters}
{
    % Identifying reactions
    \color{blue}
Displacement currents are responsible for capacitive behaviour at interfacial boundaries.
They are brought about by the redistribution of charge in response to applied fields, however they may also be a result of reversible Faradaic reactions at the surface of the electrode.
Such reactions involving water and platinum, as identified in \cite{Horch2004}, include:
    \begin{eqnarray}
        Pt + H_{2}O &\Leftrightarrow& PtO + 2\cdot H^{+} + 2 \cdot e^{-}\\
        Pt + H^{+} & \Leftrightarrow & Pt-H\\
        Pt + H_{2}O + e^{-} &\Leftrightarrow& Pt-H+OH^{-}
    \end{eqnarray}

@@

    \bibitem{Horch2004}
    K.~W.~Horsch and G.~S.~Gurpreet
    ``Neuroprosthetics: theory and practice'',
    World Scientific, 2004.

>>>>

\section{Displacement Parameters}
{
    % Identifying reactions
    \color{blue}
Displacement currents are responsible for capacitive behaviour at interfacial boundaries.
They are brought about by the redistribution of charge in response to applied fields, i.e. a charged electrode will attract or repel $Cl^{-}$ from its surface and reorientate polar molecules in the surrounding solution. This capacitive behaviour may also be a result of electrode polarisation in the form of reversible Faradaic reactions at the surface of the electrode.
Such reactions involving water and platinum, as identified in \cite{Horch2004,Mohtashami2011}, include:
    \begin{eqnarray}
        Pt + H_{2}O &\Leftrightarrow& PtO + 2 H^{+} + 2 e^{-}\\
        PtO + H_{2}O &\Leftrightarrow& PtO_{2} + 2 H^{+} + 2e^{-}\\
        Pt + H^{+} & \Leftrightarrow & Pt-H\\
        Pt + H_{2}O + e^{-} &\Leftrightarrow& Pt-H+OH^{-}
    \end{eqnarray}

@@

    \bibitem{Mohtashami2011}
    Saba~Mohtashami,
    ``ELECTROCHEMICAL PROPERTIES OF FLEXIBLE ELECTRODES FOR IMPLANTED NEUROMUSCULAR EXCITATION APPLICATIONS'',
    Open Acess Dissertations and Theses (2011), Paper 6152

    \bibitem{Horch2004}
    K.~W.~Horsch and G.~S.~Gurpreet,
    ``Neuroprosthetics: theory and practice'',
    World Scientific, 2004.
